\chapter*{Purpose Of The Manual}

This manual serves as a comprehensive guide for users of the Ostival open-source tool, which enables the simulation of Verilog designs from high-level synthesis down to physical GDS-II layout. 

The primary goal of this documentation is to empower you to:

\textbf{Understand the Tool's Capabilities:} Gain a clear insight into what Ostival can do, its core features, and the underlying open-source technologies it leverages (e.g., Icarus iVerilog, Yosys).

\textbf{Navigate the Design Flow:} Learn the step-by-step process of converting your Verilog Register-Transfer Level (RTL) code into a manufacturable GDS-II layout, including logic synthesis, place and route, and layout generation.

\textbf{Effectively Use the Tool:} Follow practical examples, tutorials, and command references to run your designs through the entire flow successfully.

\textbf{Debug and Troubleshoot:} Stuck somewhere? No problem! This document can help you identify common issues, understand error messages, and find solutions to ensure a smooth design experience.

\textbf{Contribute to the Project (Optional):} For advanced users and developers, this manual provides a comprehensive guide to every detail of the tool's architecture, allowing you to contribute to its ongoing development and improvement.

By providing detailed explanations, we aim to give the hardware development community a powerful open-source ASIC design flow tool, accessible to everyone, including students, researchers, hobbyists, and even professionals.


\vfill

Happy Designing!

Team Ostival

hello@ostival.org