\chapter*{Vision and Philosophy}

Our vision for Ostival is to democratize ASIC design, making the journey from Verilog code to a physical chip layout accessible to everyone. We believe that robust, open-source tools are fundamental to fostering innovation, education, and collaboration in the world of silicon.

We are building this tool on the following core philosophies:

\begin{itemize}
    \item \textbf{Openness and Accessibility:} We are committed to an entirely open-source approach, from the underlying design kits (like SkyWater SKY130) to every component of our toolchain. This ensures transparency, encourages scrutiny, and lowers the barrier to entry for individuals and small teams who might otherwise be excluded from chip design due to proprietary tool costs.
    \item \textbf{Integration and Cohesion:} Rather than developing every module from scratch, we strategically integrate and orchestrate best-in-class open-source EDA tools (such as Yosys, components of OpenRoad, Magic, and KLayout). Our philosophy is to provide a seamless, unified experience that simplifies the complex interactions between these powerful but disparate tools.
    \item \textbf{Usability and Documentation:} A powerful tool is only valuable if it can be used effectively. We prioritize clear, comprehensive documentation, intuitive workflows, and practical examples to ensure that users—from beginners to seasoned professionals—can quickly get started and achieve their design goals.
    \item \textbf{Community-Driven Development:} We believe in the power of collective effort. Ostival is a community project, and we welcome contributions, feedback, and ideas from users and developers worldwide. Together, we can build a tool that evolves with the needs of the open-source hardware community.
    \item \textbf{Reliability and Reproducibility:} We strive for a toolchain that produces consistent, reliable, and foundry-ready GDS-II outputs. Our aim is to provide a flow that you can trust for both learning and practical application, ensuring that what you simulate closely matches what can be fabricated.
\end{itemize}


Through these principles, Ostival aims to be more than just a piece of software; it aspires to be a catalyst for a new era of open hardware innovation.


\vfill

Happy Designing!

Team Ostival

hello@ostival.org