\chapter*{Acknowledgments}

This tool, Ostival, is the result of dedicated individual effort. However, its creation would not have been possible without the immense contributions of the broader open-source hardware and Electronic Design Automation (EDA) communities.

I extend my sincerest gratitude to:

\begin{itemize}
    \item \textbf{The Developers and Communities Behind Core Open-Source EDA Tools:} A profound thank you to the creators and maintainers of indispensable projects such as iVerilog, Yosys, Netgen, Magic VLSI Layout Tool, KLayout, and others. These pioneering tools form the very backbone of Ostival, and their existence is a testament to the power of open collaboration.
    \item \textbf{The Qt Project and Community:} For providing the robust and versatile Qt cross-platform application framework. Its powerful libraries and tools have been instrumental in developing the user interface, facilitating the visualization components, and building the foundational utilities of this tool.
    \item \textbf{The SkyWater Technology and Google Teams, and the Open-Source PDK Community:} For their groundbreaking work in open-sourcing the SkyWater SKY130 Process Design Kit (PDK). This initiative has revolutionized accessibility to chip fabrication and provides the essential physical data that enables our synthesis-to-GDS-II flow.
    \item \textbf{The Entire Open-Source Hardware Ecosystem:} To the countless individuals, researchers, and organizations who contribute to open standards, share knowledge, and foster a spirit of innovation in hardware design. Your collective efforts inspire and empower projects like this one.
\end{itemize}

While I have undertaken the development of Ostival independently, the spirit of open collaboration and the availability of these incredible resources have been invaluable. Thank you for making this project possible.


\vfill

Happy Designing!

Team Ostival

hello@ostival.org